### 2018-04-29 4_impl.tex
add support for verbatim listings of linux tree utility.

As \porthos[1], the \porthos[2] uses the open-source SMT solver \texttt{Z3} from Microsoft Research~\ref{de2008z3}. However, unlikely its predecessor, the \porthos[2] has an additional abstraction level \texttt{Z-formula} (see Section~\ref{ch:impl:model:zformula}) that allow to use any other SMT solver. %TODO: *should* allow?

@@

The general architecture scheme of \porthos[2] is presented in Figure~\ref{fig:arch}.
The program takes as input the program to be analysed and one (the reachability analysis mode) or two (the portability analysis mode) memory models. The parsed program syntax tree is then converted (Section~\ref{ch:impl:proc:y-constr}) to a program AST called \texttt{Y-tree}%
\footnote{In order to avoid confusion between different internal representations, we prefix the names of elements of each internal representation with a letter. For instance, we picked the letter `Y' to denote the AST code representation as drawing of this letter resembles the tree branching; with letter `X' we prefix elements of the event-flow graph as the events are to be e\textbf{x}ecuted; and with letter `W' we prefix elements of the \textbf{w}eak memory model AST.} %
(Section~\ref{ch:impl:model:ytree})
%, and the memory model is being parsed (Section~\ref{ch:impl:proc:w-parser}) to another AST called \texttt{W-model} (Section~\ref{ch:impl:model:wmodel}).
, which then is being pre-processed at the pre-compilation stage (Section~\ref{ch:impl:proc:x-pre-compiler}) in order to collect information necessary for the compilation.
The \texttt{Y-tree} then is being compiled (Section~\ref{ch:impl:proc:x-compiler}) to an \texttt{X-graph} representation (Section~\ref{ch:impl:model:xgraph}).
The compiled \texttt{X-graph} then undergoes a number of transformations (Section~\ref{ch:impl:proc:x-transf}) necessary for the encoding into a \texttt{Z-formula} (Section~\ref{ch:impl:model:zformula}) at the pre-encoding stage (Section~\ref{ch:impl:proc:x-transf}).
Then, the memory-model constructor (Section~\ref{ch:impl:proc:w-constr}) constructs the derived relations on the basis of the \texttt{X-graph} in order to build the weak memory model \texttt{W-model} (Section~\ref{ch:impl:model:wmodel}).
Thereafter, \texttt{W-model} and transformed \texttt{X-graph} are encoded (Section~\ref{ch:impl:proc:z-encoder}) to a \texttt{Z-formula} representation (a wrapper over an SMT logical formula), which then is passed as an input to the SMT-solver.

@@

>>>>

As \porthos[1], the \porthos[2] uses the open-source SMT solver \texttt{Z3} from Microsoft Research~\ref{de2008z3}. However, unlikely its predecessor, the \porthos[2] has an additional abstraction level \zformula (see Section~\ref{ch:impl:model:zformula}) that allow to use any other SMT solver. %TODO: *should* allow?

@@

The general architecture scheme of \porthos[2] is presented in Figure~\ref{fig:arch}.
The program takes as input the program to be analysed and one (the reachability analysis mode) or two (the portability analysis mode) memory models. The parsed program syntax tree is then converted (Section~\ref{ch:impl:proc:y-constr}) to a program AST called \ytree%
\footnote{In order to avoid confusion between different internal representations, we prefix the names of elements of each internal representation with a letter. For instance, we picked the letter `Y' to denote the AST code representation as drawing of this letter resembles the tree branching; with letter `X' we prefix elements of the event-flow graph as the events are to be e\textbf{x}ecuted; and with letter `W' we prefix elements of the \textbf{w}eak memory model AST.} %
(Section~\ref{ch:impl:model:ytree})
%, and the memory model is being parsed (Section~\ref{ch:impl:proc:w-parser}) to another AST called \wmodel (Section~\ref{ch:impl:model:wmodel}).
, which then is being pre-processed at the pre-compilation stage (Section~\ref{ch:impl:proc:x-pre-compiler}) in order to collect information necessary for the compilation.
The \ytree then is being compiled (Section~\ref{ch:impl:proc:x-compiler}) to an \xgraph representation (Section~\ref{ch:impl:model:xgraph}).
The compiled \xgraph then undergoes a number of transformations (Section~\ref{ch:impl:proc:x-transf}) necessary for the encoding into a \zformula (Section~\ref{ch:impl:model:zformula}) at the pre-encoding stage (Section~\ref{ch:impl:proc:x-transf}).
Then, the memory-model constructor (Section~\ref{ch:impl:proc:w-constr}) constructs the derived relations on the basis of the \xgraph in order to build the weak memory model \wmodel (Section~\ref{ch:impl:model:wmodel}).
Thereafter, \wmodel and transformed \xgraph are encoded (Section~\ref{ch:impl:proc:z-encoder}) to a \zformula representation (a wrapper over an SMT logical formula), which then is passed as an input to the SMT-solver.

@@

The first internal representation that \porthos[2] uses is the \ytree, which represents rather a high-level AST. Any input program (whether it is high-level \texttt{C} code or low-level assembly code) is translated to the \ytree.

\begin{paracol}{2}
text text text text text text text text text text text text

text text text text text text

text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text

text text text text text text text text text text text text text text text text text text text text text text text text text text

text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text

\switchcolumn

\VerbatimInput{inc/lst/Ytree-tree.out}
\end{paracol}

%The syntax tree of the \texttt{C} program is being desugared %examples
